---
format: gfm
execute:
  output: asis
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# biblegatewayr

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/biblegatewayr)](https://cran.r-project.org/package=biblegatewayr)
<!-- badges: end -->

The `biblegatewayr` package provides functions to interact with the BibleGateway web page. It includes `get_bible_verse` to retrieve specific verses by canonical reference (e.g., "John 3:16") and `find_bible_verse` to search for verses containing specific text. Both functions support multiple Bible versions and return formatted output, making it easy to incorporate Bible verses into markdown documents.

## Installation

You can install the development version of `biblegatewayr` from [GitHub](https://github.com/angelfelizr/biblegatewayr) with:

``` r
# install.packages("devtools")
devtools::install_github("angelfelizr/biblegatewayr")
```

Or install the latest version from CRAN:

```r
install.packages("biblegatewayr")
```

## Examples

### Get a Specific Verse

This example demonstrates how to get a specific verse using `get_bible_verse`.

```{r example_get_verse}
library(biblegatewayr)

# Get the verse John 3:16
get_bible_verse("Juan 3:16") |> cat()

# Get the verse Psalm 23
get_bible_verse("Salmos 23")
```

### Search for Verses

This example demonstrates how to search for verses containing specific text using `find_bible_verse`.

```{r example_find_verse}
# Search for verses containing "el amor es paciente"
find_bible_verse("el amor es paciente", version = "NTV") |> cat(sep = "\n\n")

# Search for verses containing "fe esperanza amor" in the NTV version
find_bible_verse("fe esperanza amor", version = "NTV")
```

## Main components

This package contains two main functions:

-   `get_bible_verse()`: Retrieves a specific Bible verse by its reference (e.g., "John 3:16").
-   `find_bible_verse()`: Searches for Bible verses based on a text query.

Both functions allow you to specify the Bible version. For more details please refer to the function documentation with `?get_bible_verse` or `?find_bible_verse`.
